Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-03-19 analysis2_manuscript.tex
Update analysis2_manuscript.tex
Co-authored-by: Andrew Kern <adkern@uoregon.edu>

    A challenge when comparing different inferred and simulated distributions of the selection coefficient ($s$)
    is differing conventions in the literature regarding its definition.
    The simulator \slim and the inference tool \grapes define the selection coefficient $s$ such that a homozygote has fitness $1+s$.
    On the other hand, \dadicli and \polydfe define the selection coefficient such that a homozygote has fitness $1+ 2s$.
    Moreover, inferred distributions of selection coefficients are typically scaled by an inferred ancestral
    effective population size $N_e$, and different methods assume different scaling.
    \dadicli infers the distribution of $2 N_e s$ while \polydfe and \grapes infer the distribution of $4 N_e s$.
    To allow direct comparison, here we have normalized all inference results to the convention of \slim
    (also used by \stdpopsim; see \textbf{Methods}).
    %IG - citations suggested in earlier versions to be added (I'm not sure they're necessary)
    % precursor of polyDFE  from 2017:     https://academic.oup.com/genetics/article/207/3/1103/5930676
    % fastDFE - the successor to polyDFE:  https://academic.oup.com/mbe/article/41/5/msae070/7641109
    % paper that uses GRAPES from 2020:    https://academic.oup.com/genetics/article/216/2/559/6066183

>>>>

    A challenge when comparing different inferred and simulated distributions of the selection coefficient ($s$)
    is differing conventions in the literature regarding its definition.
    The simulator \slim and the inference tool \grapes define the selection coefficient $s$ such that a homozygote has fitness $1+s$.
    On the other hand, \dadicli and \polydfe define the selection coefficient such that a homozygote has fitness $1+ 2s$.
    Moreover, inferred distributions of selection coefficients are typically scaled by an inferred ancestral
    effective population size $N_e$, and different methods assume different scaling.
    \dadicli infers the distribution of $2 N_e s$ while \polydfe and \grapes infer the distribution of $4 N_e s$.
    To allow direct comparison, here we have normalized all inference results to the convention used by \slim
    (also used by \stdpopsim; see \textbf{Methods}).
    %IG - citations suggested in earlier versions to be added (I'm not sure they're necessary)
    % precursor of polyDFE  from 2017:     https://academic.oup.com/genetics/article/207/3/1103/5930676
    % fastDFE - the successor to polyDFE:  https://academic.oup.com/mbe/article/41/5/msae070/7641109
    % paper that uses GRAPES from 2020:    https://academic.oup.com/genetics/article/216/2/559/6066183
